---
title: "Final Project"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, comment = "")
```

## Employees

Before the new store opens in Detroit, Cloud has already started the hiring process. Currently there are 20 people willing to work any job within the dispensary, but they have given preferences for each of the main departments. In the `job_preference_list` file, every person is listed with their preference values for each functional unit: the higher the value, the more a person would like to work in that department. Ideally, the employees are distributed equally across the functional units.


Load Necessary Packages:
```{r}
library(tidyr)
library(ompr)
library(ompr.roi)
library(ROI.plugin.glpk)
```

Load Data:
```{r}
job_preferences <- load("/Users/kcernugel/Downloads/job_preference_list.RData")
```



Notes:

- 20 employees
- 4 departments
- 5 employees in each department



Pivot Data:
```{r}
# pivot data to be wider and easier to work with
spread_data <- spread(job_preference, jobType, preference)
head(spread_data)
```
Turn Employee Name into Index:
```{r}
preference_data <- rownames(spread_data) <- spread_data$personName
```

Extract Preference Columns Only:
```{r}
preference_data <- spread_data[c("bud tending", "customer service", "marketing", "security")]
head(preference_data)
```

Set Constraints and Variables:
```{r}
employees <- as.integer(nrow(spread_data))
departments <- 4
capacity <- rep.int(5, departments)

# Function to Pull Preferences of Each Employee/Row
weight <- function(employee, department) preference_data[employee, department]
```

Build the Model:
```{r}
model <- MIPModel() %>%
  # 1 if employee i is assigned to department j
  add_variable(x[i, j], i = 1:employees, j = 1:departments, type = "binary") %>%
  
  # maximize the preferences
  set_objective(sum_expr(weight(i, j) * x[i, j], i = 1:employees, j = 1:departments)) %>%
  
  # we cannot exceed the capacity of a department (5)
  add_constraint(sum_expr(x[i, j], i = 1:employees) <= capacity[j], j = 1:departments) %>% 
  
  # each employee needs to be assigned to one department
  add_constraint(sum_expr(x[i, j], j = 1:departments) == 1, i = 1:employees)

model
```

Solve Model & Results:
```{r}
result <- solve_model(model, with_ROI(solver = "glpk"))

result <- get_solution(result, x[i, j])

result <- result[result$value == 1, c("i", "j")]

team_results <- dplyr::left_join(spread_data, result, by=c("personID"="i"))

team_results$department <- ifelse(team_results$j==1, "bud tending",
                       ifelse(team_results$j==2, "customer service",
                              ifelse(team_results$j==3, "marketing",
                                     "security")))
```

```{r}
team_results <- team_results[,c("personName", "department")]
team_results
```

```{r}
team_results[order(team_results$department),]
```
