---
title: "Final Project"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE, comment = "")
```

## Employees

Before the new store opens in Detroit, Cloud has already started the hiring process. Currently there are 20 people willing to work any job within the dispensary, but they have given preferences for each of the main departments. In the `job_preference_list` file, every person is listed with their preference values for each functional unit: the higher the value, the more a person would like to work in that department. Ideally, the employees are distributed equally across the functional units.

```{r}
# 20 employees
# 4 departments
# 5 people in each

library(tidyr)

job_preferences <- load("/Users/kcernugel/Downloads/Simulation and Optimization/job_preference_list.RData")

spread_data <- spread(job_preference, jobType, preference)
View(spread_data)
```

```{r}
library(ompr)
library(ompr.roi)
library(ROI.plugin.glpk)

employees <- nrow(spread_data)
departments <- 4
capacity <- rep.int(5, departments)

preference_data <- rownames(spread_data) <- spread_data$personName
preference_data <- spread_data[c("bud tending", "customer service", "marketing", "security")]
head(preference_data)

preferences <- function(employee) preference_data[employee,]

weight <- function(employee, department) {
  p <- which(as.numeric(department) == preferences(as.numeric(employee)))
  as.integer(if (length(p) == 0) {
    -100000
  } else {
    p
  })
}
```

```{r}
library(ompr)
model <- MIPModel() %>%
  # 1 iff student i is assigned to course m
  add_variable(x[i, j], i = 1:employees, j = 1:departments, type = "binary") %>%
  
  # maximize the preferences
  set_objective(sum_expr(weight(i, j) * x[i, j], i = 1:employees, j = 1:departments)) %>%
  
  # we cannot exceed the capacity of a course
  add_constraint(sum_expr(x[i, j], i = 1:employees) <= capacity[j], j = 1:departments) %>% 
  
  # each student needs to be assigned to one course
  add_constraint(sum_expr(x[i, j], j = 1:departments) == 1, i = 1:employees)

model
```

```{r}
result <- solve_model(model, with_ROI(solver = "glpk"))
```

```{r}
result <- get_solution(result, x[i, j])

result[result$value == 1, c("i", "j")]
```

```{r}
spread_data[result[result$value == 1, c("i", "j")],
            c("personName", "jobType")]

job_preference[result[result$value == 1, c("i", "j")],
            c("personName", "jobType")]
```

